---
title: "AquasatAndBandRatios"
author: "Mallard"
date: "11/2/2022"
output: html_document
---

Using aquasat data to assess the utility of various band ratios as relative metrics of sediment concentrations

Load libraries
```{r, echo=FALSE, message=FALSE}
#Libraries
library(tidyverse)
library(gridExtra)
library(maps)
library(ggthemes)
library(ggpubr)
library(pals)
library(hexbin)
library(broom)
library(bit64)
```

Read in data from "AquaSat" on figshare (https://figshare.com/collections/AquaSat/4506140/2) 
  and data from MR with only tss (tss_only.csv, no ssc)
  and data from JG shared via Google drive (https://drive.google.com/drive/folders/1egw_P7bJVTKZx8j_RyS_xtDwCYgdbGVN)

```{r data, echo=FALSE, message=FALSE}
aquasat_raw <- data.table::fread("data/aquasat/sr_wq_rs_join.csv") %>% 
  as_tibble()
aquasat_JG <- data.table::fread("data/aquasat/aquasat_tss_full_train.csv") %>% 
  as_tibble() %>% 
  rename(tss = value) #Rename "value" to "tss" so this dataset plugs into analysis done below for main aquasat
aquasat_tss_only <- data.table::fread("data/aquasat/tss_only.csv") %>% 
  as_tibble()
aquasat_JG_huge <- feather::read_feather("data/aquasat/parametersMunged_corrected_v4.feather") %>% 
  as_tibble() %>% 
  rename(tss = value)
```

Filter data:
- tss != NA & <= 5000
- relevant bands >= 0, <= some threshold
- pixelCount >= 9
- only "Stream" samples


Add indices:
- NDSSI:
- NSMI: 
- BR: 

```{r,  echo=FALSE, message=FALSE}
lowRef = 0 #Thresholds for reflectance from each band
hiRef = 5000

aquasat <- aquasat_raw %>% #Can change input bn aquasat_raw, aquasat_JG, aquasat_tss_only
  filter(
    !is.na(tss) & 
      blue >= lowRef & blue <= hiRef &
      nir >= lowRef & nir <= hiRef &
      red >= lowRef & red <= hiRef &
      green >= lowRef & green <= hiRef &
      tss <= 5000 &
      pixelCount >= 9 &
      type %in% c("Stream")) %>%
  mutate(., 
         NDSSI = (nir-blue)/(nir+blue), #Note that this is reversed from normal to make high NDSSI = high sediment
         NSMI = (red+green-blue)/(red+green+blue),
         BR = (green/blue)
  )
```

Look at top few sites in terms of # of samples, for all 3 indices
```{r,  echo=FALSE, message=FALSE}
countSites <- aquasat %>% 
  count(SiteID)
countSites <- countSites[order(-countSites$n),]

#All
# for(i in 1:5){
#   tempFig1 <- ggplot(aquasat[aquasat$SiteID == countSites$SiteID[i],], aes(y = tss, x = NDSSI)) + geom_point()
#   tempFig2 <- ggplot(aquasat[aquasat$SiteID == countSites$SiteID[i],], aes(y = tss, x = NSMI)) + geom_point()
#   tempFig3 <- ggplot(aquasat[aquasat$SiteID == countSites$SiteID[i],], aes(y = tss, x = BR)) + geom_point()
#   tempFig <- grid.arrange(tempFig1, tempFig2, tempFig3, nrow = 1)
# }

#NDSSI
for(i in 1:5){
  tempFig <- ggplot(aquasat[aquasat$SiteID == countSites$SiteID[i],], aes(y = tss, x = NDSSI)) + geom_point()
  print(tempFig)
}

# #NSMI
# for(i in 1:5){
#   tempFig <- ggplot(aquasat[aquasat$SiteID == countSites$SiteID[i],], aes(y = tss, x = NSMI)) + geom_point()
#   print(tempFig)
# }
# 
# #BR
# for(i in 1:5){
#   tempFig <- ggplot(aquasat[aquasat$SiteID == countSites$SiteID[i],], aes(y = tss, x = BR)) + geom_point()
#   print(tempFig)
# }

```

Regression analysis of individual sites: spearman's rho and kendall's tau

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Calculate spearman or kendall tau for all unique sites with n > some threshold
threshN <- 50
pVals <- countSites %>%
  add_column(p = numeric(nrow(countSites))) %>%
  add_column(m = numeric(nrow(countSites))) %>%
  filter(n >= threshN)

for(i in 1:nrow(pVals)){
  tempData <- aquasat %>%
    filter(SiteID == pVals$SiteID[i])
  tempFit <- cor.test(tempData$tss, tempData$NSMI, method = "spearman")
  pVals$p[i] <- tempFit$p.value
  pVals$m[i] <- tempFit$estimate[[1]]
}

nSites <- nrow(pVals)
propSites <- sum(pVals$p < 0.05 & pVals$m > 0)/nrow(pVals)
nSites
propSites
```


Plot some scatters/densities of overall data

```{r echo=FALSE, message=FALSE}
# ggplot(aquasat[aquasat$type == "Lake",], aes(y = tss, x = NDSSI)) + geom_point()
# ggplot(aquasat[aquasat$type == "Stream",], aes(y = tss, x = NDSSI)) + geom_point()
# ggplot(aquasat[aquasat$type == "Estuary",], aes(y = tss, x = NDSSI)) + geom_point()
ggplot(aquasat, aes(y = tss, x = NDSSI)) + geom_point() + stat_smooth(method = "lm", col = "red")
ggplot(aquasat, aes(y = tss, x = NSMI)) + geom_point() + stat_smooth(method = "lm", col = "red")
ggplot(aquasat, aes(y = tss, x = BR)) + geom_point() + scale_x_log10()
# ggplot(aquasat, aes(y = tss, x = red)) + geom_point()
# ggplot(aquasat, aes(y = tss, x = green)) + geom_point()
# ggplot(aquasat, aes(y = tss, x = blue)) + geom_point()
# ggplot(aquasat, aes(y = tss, x = nir)) + geom_point()

ggplot(aquasat, aes(y = tss, x = NDSSI)) + geom_hex(bins = 100) + scale_y_log10()
ggplot(aquasat, aes(y = tss, x = NSMI)) + geom_hex(bins = 100) + scale_y_log10()


```

